Variational Monte Carlo on Bosonic Systems

### 2018-04-05 project_1/article/article.tex
Spell check section on local energy

    \subsection{Local energy}
        As the many-body wavefunction creates a very large configuration space,
        where much of the wavefunction is small, we use the Metropolis algorithm
        in order to move towards regions in configuration space with
        ``sensible'' values. We define the \emph{local energy}, $E_L(\vf{r})$,
        by
        \begin{align}
            E_L(\vf{r})
            &= \frac{H\Psi_T(\vf{r})}{\Psi_T(\vf{r})}.
        \end{align}
        If $\Psi_T(\vf{r})$ is an exact eigenfunction of the Hamiltonian, $E_L$
        will be constant. The closer $\Psi_T(\vf{r})$ is to the exact wave
        function, the less variation in $E_L$ as a function of $\vf{r}$ we get.
        This leads us to searching for values of $\vf{r}$ yielding the lowest
        variance in $E_L$.

        When we are performing the Monte Carlo sampling we are interested in the
        expected value of the local energy as this will serve as our estimate of
        the true energy. Mathematically this is expressed as
        \begin{align}
            \expval{E_L}
            &=
            \frac{\int\dd \vf{r}\Psi_T^{*}(\vf{r})H\Psi_T(\vf{r})}
            {\int\dd \vf{r}|\Psi_T(\vf{r})|^2}
            =
            \frac{
                \int\dd \vf{r}|\Psi_T(\vf{r})|^2 E_L(\vf{r})
            }{
                \int\dd \vf{r}|\Psi_T(\vf{r})|^2
            },
        \end{align}
        where we have multiplied and divided by the trial wavefunction to get
        the latter expression.

        One of the most computationally intensive parts of the Variational Monte
        Carlo algorithm will be to compute $E_L$. We will therefore find an
        analytical expression for $E_L$ in terms of the trial wavefunctions and
        the system we are exploring.

>>>>

    \subsection{Local energy}
        As is mostly the case in physics, the quantity we are looking for is the
        energy. We therefore define the \emph{local energy} by
        \begin{align}
            E_L(\vf{r})
            &= \frac{H\Psi_T(\vf{r})}{\Psi_T(\vf{r})}.
        \end{align}
        The energy of the system is thus found by computing the expectation
        value of the local energy.
        \begin{align}
            \expval{E_L}
            =
            \frac{
                \int\dd \vf{r}|\Psi_T(\vf{r})|^2 E_L(\vf{r})
            }{
                \int\dd \vf{r}|\Psi_T(\vf{r})|^2
            }
            \approx
            \frac{1}{N}\sum_{i = 1}^N
            p(\vf{r}_i)E_L(\vf{r}_i).
        \end{align}
        To determine if we have found a minimum we compute the variance of the
        expectation value of the local energy.
        \begin{align}
            \sigma^2 = \langle E_L^2\rangle - \expval{E_L}^2.
        \end{align}
        One of the most computationally intensive parts of the Variational Monte
        Carlo algorithm will be to compute $E_L$. We will therefore find an
        analytical expression for $E_L$ in terms of the trial wavefunctions and
        the system we are exploring.
